\doublespacing
\section{Indoor Localisation}
While outdoor flying and testing of aerial swarms has been ignored majorly and
needs to be at greater priority, the increased efficiency and faster testing due to indoor
localisation and flying of aerial swarms should not be ignored. Indoor swarms open
new opportunities in terms of heterogeneous swarms and their aiding capabilities in
disaster scenarios. The major challenges faced in indoor swarm operations is due to
unavailability of Global Positioning System. In order to facilitate indoor localisation,
ceiling mounted cameras or wifi localisation based POZYX systems are used
generally.
One such technique is used in the WHYCON image based localisation technique
based on detection and tracking. It involves detection of white and black roundel. An
initial detection step is used to identify the position of the roundel. After that using
camera re-projection techniques and known dimensions of the inner and outer
roundels, the three dimensional position of the roundel with respect to the camera is
computed. Once detected, the roundel is relocated by template matching and particle
tracking in the subsequent frames of video in close proximity to prior position. \cite{nitsche2015whycon} 
Localisation can also be done by using multiple wifi beacons and time difference of arrival from
various sources for localisation.\cite{yang2015wifi}
However, imagery based localisation systems are more accurate and faster in
comparison.
\section{Fixed Wing Aircraft}
Multi-rotors have gained tremendous popularity amongst drones due to easier
flights, less space requirements and less crashes observed in the learning phase,
however, fixed wing aircrafts are still preferred owing to their greater efficiency,
range and endurance. The swarming of fixed wings, though achieved by Naval
Postgraduate School,\cite{nps}
is very difficult to perform for larger swarms. Thus, shifting
to a fixed wing-multirotor hybrid can help in achieving swarms having larger range
and endurance by exploiting the capabilities of both.